### 2018-07-04 paper/sphinxes.tex
Adds CLOnionRouting
Changes Sphinxes title to include "Extended for Sets"

\section{Sphinxes: the Sphinx header format for multi-node layers}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.

>>>>

\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes based on 
the formal definitions of \textcite{CLOnionRouting}.
